Using Probabilistic Knockoffs of Binary Variables to Control the False Discovery Rate

### 2015-07-29 masters_paper/presentation.tex
working on presentation

\documentclass[11pt]{article}
\usepackage[paper=letterpaper, margin=.5in]{geometry}
\linespread{1.5}
\pdfpagewidth 8.5in
\pdfpageheight 11in

%%% Packages
% First four - AMS (american mathematical society). General math goodness. I use the align* enviorment in particular
% multirow, multicol allow for certain kinds of tables
% enumerate lets you determine the style of the counter for the enumerate enviorment
% graphicx lets you include pictures
% listings lets you stick in blocks of code
% placeins defines "\FloatBarrier", which stops tables from moving around
\usepackage{amsmath, amscd, amssymb, amsthm, multirow, multicol, enumerate, graphicx, listings, placeins, caption} 
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[style=numeric,backend=biber]{biblatex}
\addbibresource{bibli.bib}

\captionsetup{font={small,singlespacing},margin=1cm}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\del}{\partial}
\newcommand{\real}{\textrm{Re }}
\newcommand{\imag}{\textrm{Im }}
\newcommand{\pd}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\deriv}[2]{\frac{d #1}{d #2}}
\newcommand{\sumk}{\sum_{k=1}^\infty}
\newcommand{\sumj}{\sum_{j=1}^\infty}
\newcommand{\sumn}{\sum_{n=0}^\infty}
\newcommand{\summ}[2]{\sum_{k=#1}^{#2}}
\newcommand{\sig}[1]{\sum_{#1 =1}^\infty}
\newcommand{\un}[1]{\bigcup_{#1 =1}^\infty}
\newcommand{\inter}[1]{\bigcap_{#1 =1}^\infty}
\newcommand{\ip}[2]{\langle #1, #2 \rangle}
\newcommand{\ipxu}{\langle x,u_j \rangle}
\newcommand{\uj}{\{u_j\}_{j=1}^\infty}
\newcommand{\B}{\mathcal{B}}

\newcommand{\p}{\mathrm{P}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\var}{\mathrm{Var}}
\newcommand{\cov}{\mathrm{Cov}}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\ST}{mbox{ s.t. }}

\newcommand{\x}{\bf x}

\newcommand{\Example}{\noindent {\bf Example. \quad} }
\newcommand{\Proof}{\noindent {\bf Proof: \quad} }
\newcommand{\Remark}{\noindent {\bf Remark. \quad} }
\newcommand{\Remarks}{\noindent {\bf Remarks. \quad} }
\newcommand{\Case}{\noindent {\underline{Case} \quad} }

@@

\newcommand{\deuc}{d_{\mathrm euc}}
\newcommand{\dtaxi}{d_{\mathrm taxi}}
\newcommand{\ddisc}{d_{\mathrm disc}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\DeclareMathOperator*{\argmin}{arg\min}

\newcommand{\hwhead}[1]{#1 \hfill Aaron Maurer \vspace{2mm} \hrule \vspace{2mm}}

\begin{document}

\noindent
\thispagestyle{empty}
\underline{\bf Master's Paper of the Department of Statistics, the University of Chicago} 
    \\~~(Internal document only, not for circulation)

\vspace{1.8in}
\begin{center}
    {\bf\LARGE Using Probabilistic Knockoffs of Binary Variables to Control the False Discovery Rate}

    \vspace{1.4in}
    {\Large Aaron Maurer}

    \vspace{1.3in}
    {\Large Advisor: Rina Foygel Barber }

\end{center}

\vspace{.6in}
{\Large Approved} ~\underline{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}

\vspace{.2in}
{\Large Date} ~\underline{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}

\vfill
\begin{center}{\large August-31, 2015}\end{center}

\newpage
\pagestyle{plain}
\setcounter{page}{1}

\begin{abstract}

    \vspace{7mm}\noindent  Variable selection for regression is a key problem in applied statistics. The knockoff filter method provides one method of variable selection for linear regression. It relies on generating 'knockoff' features, which replicate the correlation structure of the original variable; when the full path of LASSO regression is fit, the point at which a a null variable and its knockoff have nonzero coefficients will be exchangeable. However, for other GLMs, the method breaks down. I will provide an alternative method of randomly generating knockoffs for binary variables which will will satisfy the original correlation condition in expectation and offer improved performance for other GLMs. \end{abstract}

\newpage
\vspace{1.5in}
\tableofcontents

\newpage

%\title{Using Probabilistic Knockoffs of Binary Variables to Control the False Discovery Rate}
%\author{Aaron Maurer}
%\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
    Variable selection is an essential problem to fitting a regression model. For linear regression, the knockoff filter (Barber and Cand\`{e}s, 2014) offers a method of exact FDR control. However, the method as originally formulated does not extend to other generalized linear models such as logistic regression. This paper offers an extension of this method which will work with binary features in the context of linear regression, but also will extend to other GLMs.

\subsection{Knockoff Filter}
    Let us consider the consider the usual setting for linear regression, where $n$ observations of a variable of interest $y$ arise from the model
    \[\mathbf{y} = X\beta + \mathbf{z}\]
    where $\mathbf{y}\in\R^n$ are the observed values of $y$, $X \in \R^{n\times p}$ is the matrix of predictor variables, $\beta\in\R^p$ are the unknown coefficients, and $\mathbf z$ is Gaussian noise. It is important to note that a intercept vector $\mathbf 1$ is not included in $X$. For the purpose of this paper, only the case where $2p\leq n$ will be considered, though the methods can be extended to $p\leq n$. I will to refer the $j$th column of $X$ as $X_j$, which is $n$ observations of the random variable $x_j$. The random variable $x_j$ is in turn $j$th entry of the random vector valued variable $\mathbf x$. In the situation where $\beta$ is sparse and there is reason to expect that $x_j$ and $y$ are uncorrelated for many $j$, the knockoff filter is a method to select a subset of the $x_j$ which are likely correlated with $y$. \par
    The method specifically seeks to control the false discovery rate (FDR), which is the expected portion of some selection of $x_j$ which are, in fact, uncorrelated with $y$. For a procedure which chooses a subset of variables $\hat S\subseteq \{1,\ldots,p\}$, this is defined as  
    \[ \textrm{FDR} = \E\left[\frac{\vert{\{j: \beta_j=0 \; \& \; j\in\hat S\}}\vert}{\max\{\vert{\hat S}\vert,1\}} \right] \]
    FDR is controlled at level $q$ if FDR is less than $q$ irrespective of the coefficients $\beta$. \par

    The knockoff filter achieves FDR control in several steps, the first of which is creating a set of `knockoff' features $\tilde X_j$ which imitate the original $X_j$ while being less correlated with $y$. In particular, the matrix of knockoffs $\tilde X$ has the same internal correlation structure as $X$, the knockoff feature $\tilde X_j$ has the same correlation with other $X_i$ as $X_j$ does, but the correlation between $\tilde X_j$ and $X_j$ is minimized. In other words, where $ G := X^TX$, 
    \[ \tilde X^T\tilde X=G \textrm{ and } \tilde X^T X = G - \diag{\mathbf s}\]
    for some vector $s\in \R^p$ such that, where $\diag{G}$ is the vector made from the main diagonal of $G$, $\diag{G} - \mathbf s$ is small. Since $\tilde X_j$ and $X_j$ have relatively low correlation, as long as $X_j$ is created independently of $\mathbf y$, $\tilde X_j$ will have lower correlation with $\mathbf y$ than $X_j$. In the case where $X_j$ is uncorrelated with $\mathbf y$, $\tilde X_j$ will also be uncorrelated with $\mathbf y$. How these knockoffs are actually generated will be described shortly.\par
    The second step is to fit a series of Lasso model of $\mathbf y$ on the combined design matrix $X_L=[X \; \tilde X]$ so as to determine the largest value $\lambda$ at which the coefficient for each $X_j$ and $\tilde X_j$ is nonzero. The subscript $L$ refers to the large design matrix with both features and knockoffs. \footnote{Other statistics besides the $\lambda$s can also be used in the knockoff method, but are not considered in this paper} Recall, for a given $\lambda$, the estimated coefficient from the Lasso regression will be 
    \[ \beta(\lambda) = \argmin_\mathbf b \left\{\frac{1}{2}\|\mathbf y - X_L\mathbf b\|^2_2 + \lambda\|b\|_1 \right\}\]
    In the general case, the coefficient for one feature in a Lasso regression being first nonzero for a larger value of $\lambda$ than another feature is an indication that the first feature is a stronger predictor of the outcome than the second. Thus, since, by construction, the knockoff features are weaker predictors than the originals, we would expect the original features to have nonzero coefficients sooner than the knockoff features when the original is a valid predictor. On the other hand, since $\beta(\lambda)$ only depends on $X_L$ through the sufficient statistics $G_L=X_L^TX_L$ and $X_L^T\mathbf y$, for null predictors, the coefficients of the original features won't enter any sooner on average than knockoff feature. This can be seen by switching a null $X_j$ with $\tilde X_j$; by construction, $G_L$ will be unaltered, while $\E\left[X_L^T\mathbf y\right]$ will also be unchanged, since $\E[X_j^T\mathbf y]=\E[\tilde X_j^T\mathbf y]=0$. \par
   This observation leads to the final step. Let $Z_j$ be the largest $\lambda$ such that feature $j$ has a nonzero coefficient and $\tilde Z_j$ the largest $\lambda$ such that knockoff $j$ has a nonzero coefficient. Then, define $W_j$ as 
   \[ W_j = \begin{cases}   Z_j         &\mbox{if } Z_j>\tilde Z_j \\ 
                            -\tilde Z_j &\mbox{if } Z_j<\tilde Z_j \\
                            0           &\mbox{if } Z_j=\tilde Z_j \\
            \end{cases} \]
            When $X_j$ is a null predictor, $W_j$ will be symmetrically distributed around zero, and when $X_j$ is true predictor, it will have a distribution skewed positive. Since $W_j$ with large positive values are more likely to be true predictors, the knockoff filter selects the variables $\{j:W_j\geq T\}$, where $T$ is a threshold defined as
            \[ T = \min\left\{ t>0 \;: \; \frac{\vert\{j:W_j\leq -t\}\vert}{\max\{\vert\{j:W_j\geq t\}\vert,1\}}\leq q \right\} \]
            Basic logic of this method is fairly simple. Let $N_h(t)$ be the random variable for the number of null predictors with $W_j\leq t$, $N_l(t)$ be the number of null predictors with $W_j\geq t$, and $V_l(t)$ \& $V_h(t)$ be the similar number of true predictors. Since the null $W_j$ are symmetrically distributed around $0$, $\E[N_l(t)]=\E[N_h(t)]$. Thus,
            \begin{align*}
                q &\geq \E\left[ \frac{\vert\{j:W_j\leq -t\}\vert}{\max\{\vert\{j:W_j\geq t\}\vert,1\}} \right] \\
                q &\geq \E\left[ \frac{N_l(t) + V_l(t)}{\max\{N_h(t) + V_h(t),1\}} \right] \\
                q &\geq \E\left[ \frac{N_l(t)}{\max\{N_h(t) + V_h(t),1\}} \right] \\
                q &\geq \E\left[ \frac{N_h(t)}{\max\{N_h(t) + V_h(t),1\}} \right] \\
                q &\geq \textrm{FDR}
            \end{align*}
            So FDR is controlled, and since $V_l(t)$ will tend to be small, it should be controlled fairly tightly.

\subsection{Original Knockoff Features}
    The original formulation of the method offers two similar methods of constructing knockoffs. Both of these will, by construction, have exactly the property that
    \[ \tilde X^T\tilde X=G \textrm{ and } \tilde X^T X = G - \diag{\mathbf s}.\]
    For both methods, the first step is to normalize the matrix $X$ such that $X_j^TX_j=1$ for all $j$. Then, let the Gram matrix of $X_L$ is
    \[ G_L= [X\; \tilde X]^T[X\; \tilde X] = \left[ \begin{array}{cc} G & G - \diag{\mathbf s} \\ G - \diag{\mathbf s} & G \end{array}\right] \]
    $A$, the Schur complement of $G$ in $G_L$ can be calculated as 
    \[ A = 2\,\diag{\mathbf s} - \diag{\mathbf s}G^{-1}\diag{\mathbf s} \]
    For $G_L$ to exist, $G_L$ must be positive semi-definite, which happens if and only if $A$ is positive semi-definite, which happens in turn if and only if\footnote{A fleshed out version of this argument can be found in the original knockoff paper} 
    \[ \diag{\mathbf s} \succeq 0  \; \textrm{ and } \; 2G - \diag{\mathbf s} \succeq 0 \]
    Given this is true, $A$ can be factored as $A=C^TC$. Combining this with a satisfactory $\mathbf s$ and an orthonormal matrix $\tilde U\in\R^{n\times p}$ such that $\tilde U^T X = 0$, a $\tilde X$ fulfilling the desired properties can be calculated as 
    \[ \tilde X = X(I-G^{-1}\,\diag{\mathbf s}) + \tilde UC\]
    As mentioned above, $\mathbf s$ should be chosen so as to make $\diag{G}-\mathbf s$ small. Since each $X_j$ has been normalized, this means that $\diag{G}=\mathbf 1$, so $\mathbf 1 - \mathbf s$ should be minimized in accordance with the restrictions on $\mathbf s$. The two methods differ in how $\mathbf s$ is chosen:
    \begin{itemize}
        \item \textit{Equi-correlated knockoffs}: Each original features is set to have the same correlation with its knockoff by setting $\mathbf s = 2\min\{\lambda_{min}(G),1\}\mathbf 1$. For all simulations in this paper, this was the method used.
        \item \textit{SDP knockoffs}: The $\mathbf s$ which minimizes the average correlation between knockoff and original features can be found via a semi-definite programing problem:
            \begin{center}
                \begin{tabular}{r l}
                    minimize & $\|\mathbf1-\mathbf s\|_1$ \\
                    subject to & $ 0 \preceq \diag{\mathbf s} \preceq 2G $
                \end{tabular} 
            \end{center}
            This method is significantly more computationally intensive. 
    \end{itemize}

\subsection{Binary Knockoffs}
    Though the ``original" knockoff method, described above, achieves the exact desired knockoff properties, the individual values in the vector $X_j$ will have little relation to the individual values in $X_j$. In particular, these values will often have very different empirical distributions. This effect is particularly noticeable when the random variable $x_j$ is discrete but $\tilde X_j$ does not even consist of the same set of values. The end result is that for variable selection for other generalized linear models, which do not have the same sufficient statistics as linear regression which knockoffs are designed to hit, the original knockoffs will fail to control FDR. \par
    Thus, this paper offers a new method of generating knockoffs which should offer superior performance with other GLMs. In this new method, the matrix of knockoff features $\tilde X$ will be generated by row from a random vector valued variable $\mathbf{\tilde x}$, each entry $\tilde x_j$ of which will have the property $\tilde x_j \sim x_j$. This random variable will also abide by a relaxation of the original knockoff condition:
    \[ \E[\mathbf{\tilde x}^T\mathbf{\tilde x}]=G \; \textrm{ and } \; \E[\mathbf{\tilde x}^T \mathbf x \st \mathbf x] = G - \diag{\mathbf s}\]
    This will ensure that, at the very least, these knockoffs are a suitable replacement for the original knockoffs for linear regression. \par
    Generating such knockoffs for a completely general case of any $\mathbf x$ is likely infeasible. However, in the specific case where $\mathbf x$ is a random binary vector variable, this paper will demonstrate a method to generate such knockoff variables. Since binary data is extremely common in many areas, this will hopefully serve as a useful tool.

\subsection{Paper Organization}
The rest of this paper will be organized in the following fashion:
\begin{itemize}
    \item Section 2 will go into more detail about how the original knockoffs breakdown with generalized linear models. In particular, several simulations will demonstrate how they breakdown.
    \item Section 3 will develop the method and theory for generating binary knockoffs.
    \item Section 4 will discuss tests of Binary knockoffs in simulation, both in comparison to the original knockoffs with Lasso and for logistic regression by itself.
    \item Section 5 is the final section, and will contain discussion of the results as well as areas for further work.
\end{itemize}

\section{Issues With Deterministic Knockoffs} 
    The knockoff filter and $W$ statistics have a very natural extension to generalized linear models. Here, where $l(\beta\st X, \tilde X)$ is the log likelihood of coefficients $\beta$ given the model, the $L1$ regularized regression model will have estimated coefficient vector
    \[ \beta(\lambda) = \argmin_\mathbf b \left\{l(\beta\st X, \tilde X) + \lambda\|b\|_1 \right\}\]
    The $Z_j$ and $\tilde Z_j$ are then, once again, the largest $\lambda$ such that the given original or knockoff feature has a positive coefficient, and then $W_j$ is constructed exactly as before. The problem with this is that if the given GLM doesn't have the same sufficient statistics as linear regression, there is no theoretical guarantee that the knockoff filter will control FDR. This is since, for null $X_j$, there is no theory to guarantee the $Z_j$ and $\tilde Z_j$ are exchangeable, and thus $W_j$ is not guaranteed to be symmetrically distributed around $0$. \par
    \begin{figure}[h]
        \begin{center}
        \includegraphics[width=14cm]{images/entryrate_original_logit}
    \end{center}
        \caption{The mean cumulative portion of $W$ statistic which are positive by absolute rank of the value. The mean is over 1000 simulations. On the left side, the features are drawn from a random standard normal distribution. On the right side, they are drawn as Bernoulli with probability $.25$ of being 1. The top has 50 features uncorrelated with the outcome, while the bottom has 40 features uncorrelated with the outcome and 10 correlated with it.}
    \end{figure}

    To test how bad this problem is, I tested the method using original style knockoffs in logistic regression. The results can be seen in figure 1, which shows cumulatively, starting with the largest absolute value, what portion of the $W_j$ are positive. For the method to work, for the null predictors, this should be a consistent $50\%$, indicative of the desired symmetric distribution. This is particularly important for high values, which play the largest roll in selecting a threshold. We see that in the top left corner, when all features are null and normally distributed, that we almost achieve this, with only a small, but consistent, deviation from $50\%$. However, in the top right, when the predictors are binary, the null originals enter first far more often, which will result in the FDR being too high. \par
    \FloatBarrier
    This gets much worse when some true predictors are included, as shown in the bottom row of the figure. For both normal and binary predictors, the originals come in first far more often in the beginning. This will completely ruin FDR control, since the portion of null predictors will be assumed far lower than it actually is. It is worth noting that the particular shape of the curve in the diagram, with the plateau for the null predictors through 10, is partially an artifact of how the totals were tabulated. The mean through the first ten is the mean for null predictors that came in first out of both null and true predictors; since the largest ten $W_j$ will tend to be true predictors, the average over the null predictors represent the few extreme $W_j$ which managed to beat out some number of true predictors.  \par
    \begin{figure}[h]
        \includegraphics[width=14cm]{images/normalQQ}
        \caption{Normal Q-Q of original variables and knockoffs for simulation with $4$ variables and 1,000 observations}
    \end{figure}

    Upon examination, the issue seems to be that the original style knockoff features have a very different empirical distribution than the features they are imitating. This is obviously true with the binary features, but even with the normal features, the distributions differ a lot. In figure 2, the distribution of four feature and the original style knockoff are plotted against a normal distribution in Q-Q plots. As you can see, they don't match at all. This is suggestive of a solution; if the knockoff variables match the marginal distribution of the original features better, the result may be more suitable for FDR control in GLMs. \par
    \FloatBarrier

\section{Random Binary Knockoffs}
Random binary knockoffs $\mathbf{\tilde x}$, which maintain the correlation condition in expectation, fit the bill in this regard. The method to produce them is based heavily on more general methodology to random binary vector variables with internal correlation.

\subsection{Random Binary Vector Generation}
The full class of random binary vector variables on $\{0,1\}^p$ can be specified as multinomial on the $2^p$ elements of the set. However, in practice, it is generally impractical to specify or estimate all $2^p$ necessary parameters, so it is useful to, as is desirable for knockoffs, pick a method to match the first two moments. These are the mean vector $\E(\bf x)=m\in(0,1)^p$ and the cross-moment matrix $\E(\bf x\bf x^T)=M\in(0,1)^{p\times p}$. Obviously, $m_i = \p(x_i=1)$, $M_{ij} = \p(x_i=x_j=1)$, and $\mathbf m=\diag{M}$. For an arbitrary symmetric $M$ to be valid cross-moment matrix for some random binary vector variable, $M-mm^T\succeq0$, and
    \[ \max\{0,m_i+m_j -1\} \leq M_{ij} \leq \min\{m_i,m_j\}\]
    for all $i\neq j.$ Given a qualifying $M$, or observed $X$, there are then a few methods for generating additional random values.

\subsubsection{Gaussian Copula Family}
Since multivariate normal distributions are easy to randomly draw from and defined by their first two moments, an obvious choice is to use them to generate random binary vectors. This might be done by finding $\mu$ and $\Sigma$ such that for $\mathbf z\sim N_p(\mu,\Sigma)$, $x_i$ can be generated as $x_i = \mathrm{sign}(z_i)$, and have the desired first two moments. However, this is only guaranteed to be feasible in the bivariate case. For higher dimensions, this method can generally only provide random binary vectors with approximately the right moments, and the quality of the approximation quickly degenerates as $p$ increases.

\subsubsection{$\mu$-Conditionals family}
    There exists a more flexible family which will always work for arbitrary $M$ called $\mu$-conditionals. The basic idea is that the $X$ is generate sequentially as 
    \[ \p(x_{i}=1\st x_{1},...,x_{i-1}) = \mu\left(a_{ii}+\sum_{k=1}^{i-1}a_{ik}x_i\right) \]
    for some monotone function $\mu:\R\to(0,1)$. This is essentially a binomial family GLM for a link function $\mu$. If one takes all of the $a_{kj}$, they can form a lower triangular matrix $A$, and then the joint density can be expressed as

    \[ \p(\mathbf x=\mathbf \gamma) \propto \mu(\mathbf{\gamma}^T A\mathbf \gamma)\]

    If $\mu$ is chosen such that it is a bijection and differentiable, there is a unique $A$ such that $\E(\mathbf x \mathbf x^T)=M$ when generated from this model. The natural choice for $\mu$ is the logistic link function $L(x)=\frac{1}{1-e^{-x}}$, which yields the Ising model, the ``binary analogue of the multivariate normal distribution which is the maximum entropy distribution on $\R^p$ having a given covariance matrix." Additionally, it has the usual benefit that the coefficients can be viewed as a log odds ratio:
    \[a_{ij} = \log\left(\frac{\p(x_j=x_k=1)\p(x_j=x_k=0)}{\p(x_j=0,x_k=1)\p(x_j=1,x_k=0)}\right) \]
    when $i\neq j$. When $\bf x$ is generated from this model with $a_{ij}=0$, then $x_i$ and $x_j$ are conditionally independent.  \par

    There is no closed form to calculate the entries in $A$ if $p>1$, but they can be derived numerically two ways. The first of these, when one is attempting to replicate the empirical cross-moments from a data matrix $X$, $a_{1i}$ to $a_{ii}$ is by fitting successive binomial family GLM regressions. The link function is the given function $\mu$, and $X_i$ is regressed on $X_{1} \ldots X_{i-1}$ using maximum likelihood. $a_{ji}$ for $i\neq j$ will then be the coefficient on $X_j$ while $a_{ii}$ is the intercept of the regression. \par
    Otherwise, if one is just working with a desired cross-moment matrix $M$, the successive rows of $A$ can be fit via Newton-Raphson. This is performed successively on each row of $A$. If the first $i-1$ rows have been fit, then the upper left $(i-1)\times(i-1)$ sub matrix $A_{-i}$ of $A$ has already been filled. Next, $\mathbf a_i$, the first $i$ entries of the $i$th row of $A$ must be fit, while the rest of the row will be 0. This corresponds to $\mathbf m_i$, the first $i$ entries of the $i$th row of $M$. In other words, $\mathbf{m}_i = [\E(x_i x_j)]_{j=1}^{i}$. Finally, let us say that $\mathbf x_{-i}$ is the first $i-1$ entries of $\mathbf x$. $\mathbf a_i$ must satisfy 
            \begin{align*}
                \mathbf m_i &= \E\left(x_i \left[\begin{array}{c} \mathbf x_{-i} \\ x_i \end{array}\right]\right) \\
                \mathbf m_i &= \E\left(\E\left(x_i \left[\begin{array}{c} \mathbf x_{-i} \\ x_i \end{array}\right]\;\bigg \vert\; \mathbf x_{-i}\right)\right)\\
                \mathbf m_i &= \sum_{\mathbf x_{-i} \in \{0,1\}^{i-1}} \p(\mathbf x_{-i})\p(x_i=1\st \mathbf x_{-i}) \left[\begin{array}{c} \mathbf x_{-i} \\ 1 \end{array}\right] \\
            \end{align*}
            When $\mu$ is the logistic link function $L$, this is
            \[ \mathbf m_i = \sum_{\mathbf x_{-i} \in \{0,1\}^{i-1}} \frac{1}{c}L\left(\mathbf x_{-i}^TA_{-i}\mathbf x_{-i}\right) L\left(\mathbf{a}_i^T\left[\begin{array}{c} \mathbf x_{-i} \\ 1 \end{array}\right]\right)\left[\begin{array}{c} \mathbf x_{-i} \\ 1 \end{array}\right] \]
            Where $c$ is the appropriate normalizing constant. Let us define the quantity on the right in the last line as $f(\mathbf a_i)$. This equation $f(\mathbf a_i)=\mathbf{m}_i$ can be solved by successive Newton-Raphson iterations defined by 
            \[\mathbf a_i^{(k+1)} = \mathbf a_i^{(k)} - \left[J\left(\mathbf a_i^{(k)}\right) \right]^{-1}\left[f\left(\mathbf a_i^{(k)}\right)-\mathbf m_i\right] \]
            where $J$ is the Jacobian of $f$. To do so, the Jacobian matrix is calculated as 
        \[ J\left( \mathbf a_i\right) = \sum_{\mathbf x_{-i} \in \{0,1\}^{i-1}} \frac{1}{c}L \left(\mathbf x_{-i}^TA_{-i}\mathbf x_{-i}\right) L'\left(\mathbf{a}_i^T\left[\begin{array}{c} \mathbf x_{-i} \\ 1 \end{array}\right]\right)\left[\begin{array}{c} \mathbf x_{-i} \\ 1 \end{array}\right]\left[\begin{array}{cc} \mathbf x_{-i}^T & 1 \end{array}\right] \]
            With $2^{i-1}$ possible values for $\mathbf x_{-i}$, this can quickly become computationally expensive. Instead, with a series of values $\mathbf x_{-i}^{(k)}\sim \mathbf x_{-i}$, the simulated values 
            \[f\left(\mathbf a_i\right) \approx \frac{1}{K}\sum_{k=1}^K L\left(\mathbf{a}_i^T\left[\begin{array}{c} \mathbf x_{-i}^{(k)} \\ 1 \end{array}\right]\right)\left[\begin{array}{c} \mathbf x_{-i}^{(k)} \\ 1 \end{array}\right] \]
            and
            \[J\left( \mathbf a_i\right) \approx \frac{1}{K}\sum_{k=1}^K L'\left(\mathbf{a}_i^T\left[\begin{array}{c} \mathbf x_{-i}^{(k)} \\ 1 \end{array}\right]\right)\left[\begin{array}{c} \mathbf x_{-i}^{(k)} \\ 1 \end{array}\right]\left[\begin{array}{cc} \mathbf [x_{-i}^{(k)}]^T & 1 \end{array}\right] \]
            can be used. \par

>>>>

\documentclass{beamer}
\usetheme{umbc1}

%%% Packages
% First four - AMS (american mathematical society). General math goodness. I use the align* enviorment in particular
% multirow, multicol allow for certain kinds of tables
% enumerate lets you determine the style of the counter for the enumerate enviorment
% graphicx lets you include pictures
% listings lets you stick in blocks of code
% placeins defines "\FloatBarrier", which stops tables from moving around
\usepackage{amsmath, amscd, amssymb, amsthm, multirow, multicol, enumerate, graphicx, listings, placeins} 
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\del}{\partial}
\newcommand{\real}{\textrm{Re }}
\newcommand{\imag}{\textrm{Im }}
\newcommand{\pd}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\deriv}[2]{\frac{d #1}{d #2}}
\newcommand{\sumk}{\sum_{k=1}^\infty}
\newcommand{\sumj}{\sum_{j=1}^\infty}
\newcommand{\sumn}{\sum_{n=0}^\infty}
\newcommand{\summ}[2]{\sum_{k=#1}^{#2}}
\newcommand{\sig}[1]{\sum_{#1 =1}^\infty}
\newcommand{\un}[1]{\bigcup_{#1 =1}^\infty}
\newcommand{\inter}[1]{\bigcap_{#1 =1}^\infty}
\newcommand{\ip}[2]{\langle #1, #2 \rangle}
\newcommand{\ipxu}{\langle x,u_j \rangle}
\newcommand{\uj}{\{u_j\}_{j=1}^\infty}
\newcommand{\B}{\mathcal{B}}

\newcommand{\E}{\mathrm{E}}
\newcommand{\var}{\mathrm{Var}}
\newcommand{\cov}{\mathrm{Cov}}
\newcommand{\ST}{mbox{ s.t. }}

@@

\newcommand{\deuc}{d_{\mathrm euc}}
\newcommand{\dtaxi}{d_{\mathrm taxi}}
\newcommand{\ddisc}{d_{\mathrm disc}}

\newcommand{\hwhead}[1]{#1 \hfill Aaron Maurer \vspace{2mm} \hrule \vspace{2mm}}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\DeclareMathOperator*{\argmin}{arg\min}

\title{Using Probabilistic Knockoffs of Binary Variables to Control the False Discovery Rate}
\author{Aaron Maurer}
\date{July 29th, 2015}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]
    \titlepage
\end{frame}

\begin{frame}{Overview}
    \begin{enumerate} 
        \item Original Knockoffs: What They Do and Where They Fail
        \item Making Knockoffs Work With GLMs
        \item Random Binary Knockoffs: The Theory
        \item Random Binary Knockoffs: Performance
        \item Where to next?
    \end{enumerate}
\end{frame}

\begin{frame}{Variable Selection in Linear Regression}
    Assume
     \[\mathbf{y} = X\beta + \mathbf{z}\]
    where $\mathbf{y}\in\R^n$, $X \in \R^{n\times p}$, $\beta\in\R^p$, and $\mathbf z$ is Gaussian noise. Also, assume sparsity:
    \[\beta_i = 0 \quad \forall i\not\in S\]
    How do we pick estimate $\hat S$?
\end{frame}

\begin{frame}{False Discover Rate}
    A common goal for a method that generates $\hat S$ is to control the false discovery rate
    \[ \textrm{FDR} = \E\left[\frac{\vert{\{j: \beta_j=0 \; \& \; j\in\hat S\}}\vert}{\max\{\vert{\hat S}\vert,1\}} \right] \]
    In other words, control portion of elements in $\hat S$ which aren't in $S$. \par
    \vspace{1cm}
    FDR is controlled at level $q$ if $q<$FDR irrespective of true $\beta$.

\end{frame}

\begin{frame}{Knockoffs}
    Knockoff variables can be used to control FDR in linear regression. 
    \begin{itemize}
        \item The idea is to create a forgery of each variable; if the forgeries seem about as good predictors as the originals, the originals are lousy predictors.
        \item For each variable $X_i$, create a knockoff feature $\tilde X_i$. Such that. 
            \[ \tilde X^T \tilde X = X^T X \quad \& \quad X^T \tilde X = X^T X - \diag{\mathbf s} \]
            Where $\diag{X^T X} - s$ is small but $\diag{X^T X} - s\succeq0$
        \item $\tilde X_i$ and $X_i$ will have same correlation with other variables, but only low correlation with each other.
        \item Given $\mathbf s$, $\tilde X$ can be generated via a rotation of $X$.
    \end{itemize}
\end{frame}

\begin{frame}{Knockoff Filter}
    These knockoffs can be used in the knockoff filter method. 
    \begin{itemize}
        \item Fit full path of LASSO regression on $[\,X\,\tilde X\,]$.
    \[ \beta(\lambda) = \argmin_\mathbf b \left\{\frac{1}{2}\|\mathbf y - X_L\mathbf b\|^2_2 + \lambda\|b\|_1 \right\}\]
        \item $Z_i$, $\tilde Z_i$ largest $\lambda$ such that $X_i$, $\tilde X_i$ have nonzero coefficient.
        \item $W_i= Z_i$ if $Z_i>\tilde Z_i$, otherwise $W_i = -\tilde Z_i$.
        \item Since $[\, X \, \tilde X\,]^T[\, X \, \tilde X\,]$ \& $[\, X \, \tilde X\,]^T\mathbf y$ sufficient statistics for $\beta(\lambda)$, $W_i$ symmetrically distributed around $0$ when $X_i$ null predictor.
        \item Thus, FDR controlled when $\hat S = \{i:W_i>T\}$ for 
            \[ T = \min\left\{ t>0 \;: \; \frac{\vert\{j:W_j\leq -t\}\vert}{\max\{\vert\{j:W_j\geq t\}\vert,1\}}\leq q \right\} \]
    \end{itemize}
\end{frame}

\begin{frame}{Where Knockoff Filter Fails}
    Knockoff filter don't work for other GLMs. \\
    \begin{center}
        \includegraphics[width=8cm]{images/entryrate_original_logit}
    \end{center}
\end{frame}

\begin{frame}{Can Knockoffs Be Fixed for GLMs?}
    \begin{itemize}
        \item Other GLMs don't have the same sufficient statistics as linear regression.
        \item Original Knockoffs don't remotely have same distribution as $X$, so ``look'' different than real variables.
        \item Knockoffs will likely work better if they have the same marginal distribution as originals. 
        \item For $X_i$ with arbitrary distribution, unclear how this might be accomplished.
    \end{itemize}
\end{frame}

\begin{frame}{Random Binary Knockoffs}
    \begin{itemize}
        \item A useful 
    \end{itemize}
\end{frame}

\end{document}
